Trends of SDR in Thessaloniki

### 2023-11-02 Article.Rmd
Commit 2023-11-02 15:08

abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
  While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
  Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
  We studied 29 years of CM-21 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
  We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
  We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.

@@

The shortwave downward solar irradiance (SDR) at Earth's surface play a significant role, on its climate.
Changes of the SDR can be related to changes on Earth's energy budget, the mechanisms of climate change, and water and carbon cycle [@Wild2009].
Can also affect, solar and agricultural production, and all living organisms.
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world on different time periods.
The term 'brightening' is generally used to describe periods of positive SDR trend, and 'dimming' for negative trend.
There are many cases on the long term records of irradiance, showing a systematic change of SDR's trend slope, occurring roughly at the last decades of the 20th century.
<!-- Trends china -->
On multiple station in China, a dimming period was reported until about 2000, followed by a brightening period [@Yang2021]. 
<!-- Trends Europe Brazil -->
A similar pattern was identified, with the breaking point around 1980, for stations in Central Europe [@Wild2021] and Brazil [@Yamasoe2021].
<!-- Trends Global -->
Also, on global scale, an AI aided continental level spatial analysis, with data from multiple station, reach similar conclusions for the above regions and for the global trend [@Yuan2021].

@@

The SDR data were measured with a Kipp & Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki 
($40^\circ\,38'\,$N, $22^\circ\,57'\,$E, $80\,$m\ a.s.l.)
in the period from 
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS$Date)`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS$Date)`.
<!-- }. -->
The monitoring site is located near the city centre, and we expect to be affected by the urban environment. 
During the study period, the pyranometer has been independently calibrated three times at the Meteorologisches Observatorium Lindenberg, DWD, when it was verified the stability of the instrument to within better than $0.7\%$ relative to the initial calibration by the manufacturer. 
Along with SDR, the direct beam radiation (DNI) was also measured by a collocated Kipp & Zonen CHP-1 pyrheliometer, for the period
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.
<!-- }. -->
Although, we have performed a similar analysis to the DNI data the results are not presented here, as they lack the appropriate statistical significance, due to the sorter duration of the data. 
However, the DNI data were used as auxiliary data, in the clear sky identification algorithm (CSid), which is discussed later, for the selection of the appropriate thresholds.
It is noted that despite the capability of the CSid algorithm to use the DNI as a characterization parameter, we haven't utilized it here, to avoid any selection bias, due to unequal length of the two datasets. 
There are four distinct steps in the creation of the dataset analysed here:
a)\ the acquisition of radiation measurements from the sensors,
b)\ the data quality check,
c)\ the identification of "clear sky" conditions from the radiometric data, and 
d)\ the aggregation of data and trend analysis.

@@

<!-- b) Radiation data quality check -->
A manual screening was performed, to remove inconsistent and erroneous recordings that can occur stochastically or systematically, during the continuous operation of the instruments.
The manual screening is aided by a radiation data quality assurance procedure, adjusted for the site, which is based on the methods of 
Long and Shi\ [-@Long2008a; -@Long2006].
Thus, problematic recordings have been excluded from further processing. 
Although it is impossible to detect all false data, the large number of available data, and the aggregation scheme we used, ensures the good quality of the radiometric measurements used in this study.

<!-- c) Clear sky identification -->
In order to be able to estimate the effect of the sky condition on the long term variability of SDR, we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition (i.e., all-sky, clear-sky and cloudy-sky).
To identify the clear-sky conditions we used a method proposed by
@Long2000
and by
@Reno2016,
which was adapted and configured for the site, as the authors suggest.

>>>>

abstract: |
  The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms. 
  Observations of SDR at different locations around the world with different environmental characteristics have been used to investigate its long-term variability and trends at different time scales. 
  Periods of positive trends are referred as brightening periods and of negative trends as dimming periods. 
  Here we studied 29 years of pyranometer data in Thessaloniki, Greece, under three types of sky conditions (clear sky, cloudy sky and all sky). 
  The clear-sky data were identified by applying a cloud screening algorithm. We found a positive trend of $0.38\,\%/\text{year}$ for all-sky, $0.35\,\%/\text{year}$ for clear-sky conditions, and $-0.28\,\%/\text{year}$ for cloudy conditions. 
  We have also investigated the consistency of these trends, the effect of the solar zenith angle, and their seasonal variability. 
  Finally, we identified some anomalies in the long term SDR trends for all sky conditions.

@@

The shortwave downward solar irradiance (SDR) at Earth's surface plays a significant role, on its climate.
Changes of the SDR can be related to changes on Earth's energy budget, the mechanisms of climate change, and water and carbon cycles [@Wild2009].
It can also affect solar and agricultural production, and all living organisms.
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world on different time periods.
The term 'brightening' is generally used to describe periods of positive SDR trend, and 'dimming' for negative trend.
There are many cases in the long term records of irradiance, showing a systematic change of SDR's trend slope, occurring roughly at the last decades of the 20th century.
<!-- Trends china -->
On multiple station in China, a dimming period was reported until about 2000, followed by a brightening period [@Yang2021]. 
<!-- Trends Europe Brazil -->
A similar pattern was identified, with the breaking point around 1980, for stations in Central Europe [@Wild2021] and Brazil [@Yamasoe2021].
<!-- Trends Global -->
Also, on global scale, an AI aided continental level spatial analysis, with data from multiple station, reach similar conclusions for the above regions and for the global trend [@Yuan2021].

@@

The SDR data were measured with a Kipp & Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki 
($40^\circ\,38'\,$N, $22^\circ\,57'\,$E, $80\,$m\ a.s.l.)
in the period from 
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS$Date)`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS$Date)`.
<!-- }. -->
The monitoring site is located near the city centre, and we expect to be affected by the urban environment. 
During the study period, the pyranometer has been independently calibrated three times at the Meteorologisches Observatorium Lindenberg, DWD, when it was verified the stability of the instrument to within better than $0.7\%$ relative to the initial calibration by the manufacturer. 
Along with SDR, the direct beam radiation (DNI) was also measured by a collocated Kipp & Zonen CHP-1 pyrheliometer, for the period
<!-- \mbox{ -->
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`
<!-- } -->
to
<!-- \mbox{ -->
`r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.
<!-- }. -->
Although, we have performed a similar analysis to the DNI data, the results are not presented here, as they lack the appropriate statistical significance, due to the sorter duration of the data. 
However, the DNI data were used as auxiliary data, in the clear sky identification algorithm (CSid), which is discussed later, for the selection of the appropriate thresholds.
It is noted that despite the capability of the CSid algorithm to use the DNI as a characterization parameter, we haven't utilized it here, to avoid any selection bias, due to unequal length of the two datasets. 
There are four distinct steps in the creation of the dataset analysed here:
a)\ the acquisition of radiation measurements from the sensors,
b)\ the data quality check,
c)\ the identification of "clear sky" conditions from the radiometric data, and 
d)\ the aggregation of data and trend analysis.

@@

<!-- b) Radiation data quality check -->
A manual screening was performed, to remove inconsistent and erroneous recordings that can occur stochastically or systematically, during the continuous operation of the instruments.
The manual screening is aided by a radiation data quality assurance procedure, adjusted for the site, which is based on the methods of 
Long and Shi\ [-@Long2008a; -@Long2006].
Thus, problematic recordings have been excluded from further processing. 
Although it is impossible to detect all false data, the large number of available data, and the aggregation scheme we used, ensures the good quality of the radiation measurements used in this study.

<!-- c) Clear sky identification -->
In order to be able to estimate the effect of the sky conditions on the long term variability of SDR, we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition (i.e., all-sky, clear-sky and cloudy-sky).
To identify the clear-sky conditions we used a method proposed by
@Long2000
and by
@Reno2016,
which were adapted and configured for the site, as the authors suggest.

### 2023-11-02 Article_A.tex
Commit 2023-11-02 15:08

\begin{document}
\maketitle
\begin{abstract}
The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
While monitoring the long term variability, there are observations of upward and downward SDR trends on different locations around the world for different time periods.
Periods of positive tredns are refered as brightening periods and with negative tredns as dimming periods.
We studied 29 years of CM-21 data from Thessaloniki, Greece, under three sky conditions (clear sky, cloudy sky and all sky conditions), applying a cloud sky identification algorithm.
We found a positive trend for all-sky and clear-sky conditions, and also, investigated the consistency of those trends, the effect of the solar zenith angle, and the variation of the trends for the seasons of the year.
We indentified that there are some anomalies in the long term SDR trends, for all sky conditions.
\end{abstract}

@@

The shortwave downward solar irradiance (SDR) at Earth's surface play a significant role, on its climate.
Changes of the SDR can be related to changes on Earth's energy budget, the mechanisms of climate change, and water and carbon cycle (Wild 2009).
Can also affect, solar and agricultural production, and all living organisms.
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world on different time periods.
The term `brightening' is generally used to describe periods of positive SDR trend, and `dimming' for negative trend.
There are many cases on the long term records of irradiance, showing a systematic change of SDR's trend slope, occurring roughly at the last decades of the 20th century.
On multiple station in China, a dimming period was reported until about 2000, followed by a brightening period (Yang et al. 2021).
A similar pattern was identified, with the breaking point around 1980, for stations in Central Europe (Wild et al. 2021) and Brazil (Yamasoe et al. 2021).
Also, on global scale, an AI aided continental level spatial analysis, with data from multiple station, reach similar conclusions for the above regions and for the global trend (Yuan, Leirvik, and Wild 2021).

@@

The SDR data were measured with a Kipp \& Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki
(\(40^\circ\,38'\,\)N, \(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.)
in the period from
1993-04-13
to
2023-04-13.
The monitoring site is located near the city centre, and we expect to be affected by the urban environment.
During the study period, the pyranometer has been independently calibrated three times at the Meteorologisches Observatorium Lindenberg, DWD, when it was verified the stability of the instrument to within better than \(0.7\%\) relative to the initial calibration by the manufacturer.
Along with SDR, the direct beam radiation (DNI) was also measured by a collocated Kipp \& Zonen CHP-1 pyrheliometer, for the period
2016-04-01
to
2023-04-13.
Although, we have performed a similar analysis to the DNI data the results are not presented here, as they lack the appropriate statistical significance, due to the sorter duration of the data.
However, the DNI data were used as auxiliary data, in the clear sky identification algorithm (CSid), which is discussed later, for the selection of the appropriate thresholds.
It is noted that despite the capability of the CSid algorithm to use the DNI as a characterization parameter, we haven't utilized it here, to avoid any selection bias, due to unequal length of the two datasets.
There are four distinct steps in the creation of the dataset analysed here:
a)~the acquisition of radiation measurements from the sensors,
b)~the data quality check,
c)~the identification of ``clear sky'' conditions from the radiometric data, and
d)~the aggregation of data and trend analysis.

@@

A manual screening was performed, to remove inconsistent and erroneous recordings that can occur stochastically or systematically, during the continuous operation of the instruments.
The manual screening is aided by a radiation data quality assurance procedure, adjusted for the site, which is based on the methods of
Long and Shi~(2008, 2006).
Thus, problematic recordings have been excluded from further processing.
Although it is impossible to detect all false data, the large number of available data, and the aggregation scheme we used, ensures the good quality of the radiometric measurements used in this study.

In order to be able to estimate the effect of the sky condition on the long term variability of SDR, we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition (i.e., all-sky, clear-sky and cloudy-sky).
To identify the clear-sky conditions we used a method proposed by
Long and Ackerman (2000)
and by
Reno and Hansen (2016),
which was adapted and configured for the site, as the authors suggest.

>>>>

\begin{document}
\maketitle
\begin{abstract}
The shortwave downward solar irradiance (SDR) is an important factor that drives climate processes, production and can affect all living organisms.
Observations of SDR at different locations around the world with different environmental characteristics have been used to investigate its long-term variability and trends at different time scales.
Periods of positive trends are referred as brightening periods and of negative trends as dimming periods.
Here we studied 29 years of pyranometer data in Thessaloniki, Greece, under three types of sky conditions (clear sky, cloudy sky and all sky).
The clear-sky data were identified by applying a cloud screening algorithm. We found a positive trend of \(0.38\,\%/\text{year}\) for all-sky, \(0.35\,\%/\text{year}\) for clear-sky conditions, and \(-0.28\,\%/\text{year}\) for cloudy conditions.
We have also investigated the consistency of these trends, the effect of the solar zenith angle, and their seasonal variability.
Finally, we identified some anomalies in the long term SDR trends for all sky conditions.
\end{abstract}

@@

The shortwave downward solar irradiance (SDR) at Earth's surface plays a significant role, on its climate.
Changes of the SDR can be related to changes on Earth's energy budget, the mechanisms of climate change, and water and carbon cycles (Wild 2009).
It can also affect solar and agricultural production, and all living organisms.
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world on different time periods.
The term `brightening' is generally used to describe periods of positive SDR trend, and `dimming' for negative trend.
There are many cases in the long term records of irradiance, showing a systematic change of SDR's trend slope, occurring roughly at the last decades of the 20th century.
On multiple station in China, a dimming period was reported until about 2000, followed by a brightening period (Yang et al. 2021).
A similar pattern was identified, with the breaking point around 1980, for stations in Central Europe (Wild et al. 2021) and Brazil (Yamasoe et al. 2021).
Also, on global scale, an AI aided continental level spatial analysis, with data from multiple station, reach similar conclusions for the above regions and for the global trend (Yuan, Leirvik, and Wild 2021).

@@

The SDR data were measured with a Kipp \& Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki
(\(40^\circ\,38'\,\)N, \(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.)
in the period from
1993-04-13
to
2023-04-13.
The monitoring site is located near the city centre, and we expect to be affected by the urban environment.
During the study period, the pyranometer has been independently calibrated three times at the Meteorologisches Observatorium Lindenberg, DWD, when it was verified the stability of the instrument to within better than \(0.7\%\) relative to the initial calibration by the manufacturer.
Along with SDR, the direct beam radiation (DNI) was also measured by a collocated Kipp \& Zonen CHP-1 pyrheliometer, for the period
2016-04-01
to
2023-04-13.
Although, we have performed a similar analysis to the DNI data, the results are not presented here, as they lack the appropriate statistical significance, due to the sorter duration of the data.
However, the DNI data were used as auxiliary data, in the clear sky identification algorithm (CSid), which is discussed later, for the selection of the appropriate thresholds.
It is noted that despite the capability of the CSid algorithm to use the DNI as a characterization parameter, we haven't utilized it here, to avoid any selection bias, due to unequal length of the two datasets.
There are four distinct steps in the creation of the dataset analysed here:
a)~the acquisition of radiation measurements from the sensors,
b)~the data quality check,
c)~the identification of ``clear sky'' conditions from the radiometric data, and
d)~the aggregation of data and trend analysis.

@@

A manual screening was performed, to remove inconsistent and erroneous recordings that can occur stochastically or systematically, during the continuous operation of the instruments.
The manual screening is aided by a radiation data quality assurance procedure, adjusted for the site, which is based on the methods of
Long and Shi~(2008, 2006).
Thus, problematic recordings have been excluded from further processing.
Although it is impossible to detect all false data, the large number of available data, and the aggregation scheme we used, ensures the good quality of the radiation measurements used in this study.

In order to be able to estimate the effect of the sky conditions on the long term variability of SDR, we created three datasets, by characterizing each one-minute measurement with a corresponding sky condition (i.e., all-sky, clear-sky and cloudy-sky).
To identify the clear-sky conditions we used a method proposed by
Long and Ackerman (2000)
and by
Reno and Hansen (2016),
which were adapted and configured for the site, as the authors suggest.

### 2023-11-02 MDPI_submition.Rmd
Commit 2023-11-02 15:08

x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom")           %>%
    kable_styling(latex_options = c('striped', 'hold_position'), full_width = TRUE) %>%
    column_spec(1, width = "8em")

>>>>

suppressMessages(
x_latex %>%
    collapse_rows(columns = 1, valign = "middle", latex_hline = "custom")           %>%
    kable_styling(latex_options = c('striped', 'hold_position'), full_width = TRUE) %>%
    column_spec(1, width = "8em")
)

### 2023-11-02 MDPI_submition.tex
Commit 2023-11-02 15:08

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The shortwave downward solar irradiance (SDR) is an important
factor that drives climate processes, production and can affect all
living organisms. While monitoring the long term variability, there are
observations of upward and downward SDR trends on different locations
around the world for different time periods. Periods of positive tredns
are refered as brightening periods and with negative tredns as dimming
periods. We studied 29 years of CM-21 data from Thessaloniki, Greece,
under three sky conditions (clear sky, cloudy sky and all sky
conditions), applying a cloud sky identification algorithm. We found a
positive trend for all-sky and clear-sky conditions, and also,
investigated the consistency of those trends, the effect of the solar
zenith angle, and the variation of the trends for the seasons of the
year. We indentified that there are some anomalies in the long term SDR
trends, for all sky conditions.}

@@

The shortwave downward solar irradiance (SDR) at Earth's surface play a
significant role, on its climate. Changes of the SDR can be related to
changes on Earth's energy budget, the mechanisms of climate change, and
water and carbon cycle \citep{Wild2009}. Can also affect, solar and
agricultural production, and all living organisms. Studies of SDR
variability, have identified some distinct SDR trends on different
regions of the world on different time periods. The term `brightening'
is generally used to describe periods of positive SDR trend, and
`dimming' for negative trend. There are many cases on the long term
records of irradiance, showing a systematic change of SDR's trend slope,
occurring roughly at the last decades of the 20th century. On multiple
station in China, a dimming period was reported until about 2000,
followed by a brightening period \citep{Yang2021}. A similar pattern was
identified, with the breaking point around 1980, for stations in Central
Europe \citep{Wild2021} and Brazil \citep{Yamasoe2021}. Also, on global
scale, an AI aided continental level spatial analysis, with data from
multiple station, reach similar conclusions for the above regions and
for the global trend \citep{Yuan2021}.

@@

A manual screening was performed, to remove inconsistent and erroneous
recordings that can occur stochastically or systematically, during the
continuous operation of the instruments. The manual screening is aided
by a radiation data quality assurance procedure, adjusted for the site,
which is based on the methods of Long and
Shi~\citetext{\citeyear{Long2008a}; \citeyear{Long2006}}. Thus,
problematic recordings have been excluded from further processing.
Although it is impossible to detect all false data, the large number of
available data, and the aggregation scheme we used, ensures the good
quality of the radiometric measurements used in this study.

In order to be able to estimate the effect of the sky condition on the
long term variability of SDR, we created three datasets, by
characterizing each one-minute measurement with a corresponding sky
condition (i.e., all-sky, clear-sky and cloudy-sky). To identify the
clear-sky conditions we used a method proposed by \citet{Long2000} and
by \citet{Reno2016}, which was adapted and configured for the site, as
the authors suggest.

@@

\begin{verbatim}
Usually it is recommended to use column_spec before collapse_rows, especially in LaTeX, to get a desired result. 
\end{verbatim}

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{The shortwave downward solar irradiance (SDR) is an important
factor that drives climate processes, production and can affect all
living organisms. Observations of SDR at different locations around the
world with different environmental characteristics have been used to
investigate its long-term variability and trends at different time
scales. Periods of positive trends are referred as brightening periods
and of negative trends as dimming periods. Here we studied 29 years of
pyranometer data in Thessaloniki, Greece, under three types of sky
conditions (clear sky, cloudy sky and all sky). The clear-sky data were
identified by applying a cloud screening algorithm. We found a positive
trend of \(0.38\,\%/\text{year}\) for all-sky, \(0.35\,\%/\text{year}\)
for clear-sky conditions, and \(-0.28\,\%/\text{year}\) for cloudy
conditions. We have also investigated the consistency of these trends,
the effect of the solar zenith angle, and their seasonal variability.
Finally, we identified some anomalies in the long term SDR trends for
all sky conditions.}

@@

The shortwave downward solar irradiance (SDR) at Earth's surface plays a
significant role, on its climate. Changes of the SDR can be related to
changes on Earth's energy budget, the mechanisms of climate change, and
water and carbon cycles \citep{Wild2009}. It can also affect solar and
agricultural production, and all living organisms. Studies of SDR
variability, have identified some distinct SDR trends on different
regions of the world on different time periods. The term `brightening'
is generally used to describe periods of positive SDR trend, and
`dimming' for negative trend. There are many cases in the long term
records of irradiance, showing a systematic change of SDR's trend slope,
occurring roughly at the last decades of the 20th century. On multiple
station in China, a dimming period was reported until about 2000,
followed by a brightening period \citep{Yang2021}. A similar pattern was
identified, with the breaking point around 1980, for stations in Central
Europe \citep{Wild2021} and Brazil \citep{Yamasoe2021}. Also, on global
scale, an AI aided continental level spatial analysis, with data from
multiple station, reach similar conclusions for the above regions and
for the global trend \citep{Yuan2021}.

@@

A manual screening was performed, to remove inconsistent and erroneous
recordings that can occur stochastically or systematically, during the
continuous operation of the instruments. The manual screening is aided
by a radiation data quality assurance procedure, adjusted for the site,
which is based on the methods of Long and
Shi~\citetext{\citeyear{Long2008a}; \citeyear{Long2006}}. Thus,
problematic recordings have been excluded from further processing.
Although it is impossible to detect all false data, the large number of
available data, and the aggregation scheme we used, ensures the good
quality of the radiation measurements used in this study.

In order to be able to estimate the effect of the sky conditions on the
long term variability of SDR, we created three datasets, by
characterizing each one-minute measurement with a corresponding sky
condition (i.e., all-sky, clear-sky and cloudy-sky). To identify the
clear-sky conditions we used a method proposed by \citet{Long2000} and
by \citet{Reno2016}, which were adapted and configured for the site, as
the authors suggest.

@@
